### 2017-06-01 gpu-04-03-accelerator.tex
Some text thingies

Since the algorithm is memory-bound, many of the optimizations we implemented
are concerned with
memory usage. For starters, we offer a fast, memory-efficient hash table on the GPU,
taylored towards
the algorithm's usage patterns. Some optimizations reduce the total memory
footprint of the algorithm. Other
optimizations explore the opportunities offered by the faster regions of the
GPU memory hierarchy: data can be put into GPU shared memory, into thread-local
memory, or in registers which requires a more complicated analysis. One
other optimization is exploitation of the vectorization possibilities.

The state for the combination of $\pi$ and $\phi$ is permanently
stored in GPU memory, because copying of the relevant portions of these
data structures to the GPU in each iteration is too costly compared to the amount
of computation. The graph is stored at the host, because mini-batch
selection is cheap, and the data required for a minibatch is small.

>>>>

Since the algorithm is memory-bound, many of the optimizations we implemented
are concerned with
memory usage. For starters, we describe our fast, memory-efficient hash table on the GPU,
taylored towards
the algorithm's usage patterns. Then some optimizations reduce the total memory
footprint of the algorithm. Other
optimizations explore the opportunities offered by the faster regions of the
GPU memory hierarchy: data can be put into GPU shared memory, into thread-local
memory, or in registers which requires a more complicated analysis. One
other optimization is exploitation of the vectorization possibilities.

The state for the combination of $\pi$ and $\phi$ is permanently
stored in GPU memory, because copying of the relevant portions of these
data structures to the GPU in each iteration is too costly compared to the amount
of computation. The graph is stored both at the host and in GPU memory. The
host draws the mini-batches, because that operation is cheap,
and the data required for a minibatch is small.
